\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{babel}

\usepackage[usenames, dvipsnames]{color}
\definecolor{lgrey}{gray}{0.6} % gray stands for the grey scale
\definecolor{dgrey}{gray}{0.4}
\definecolor{lblue}{RGB}{79,129,189}

% Define commands

% hspace
\newcommand{\tab}[1][1cm]{\hspace*{#1}}

% Section Header
\newcommand{\header}[1]{
    \vspace*{-2mm}
    \rule{6.5in}{3pt} \\
    \smallskip
    \begin{large}
	    \textsc{\textcolor{lblue}{#1}}
    \end{large}
    \bigskip
}

% Company Name, Location, Start, End
\newcommand{\company}[4]{
    \textsc{\textbf{#1}} \tab \small {#2} \hfill \small {#3 {-} #4} \\
    \medskip
}

% Job Title, Start, End, Technologies used
\newcommand{\position}[4]{
    \tab[0.5cm] \textbf{#1} \hfill {\footnotesize #2 {-} #3 \par}
    \tab[1cm] \textit{Technology Used:} #4 \\
    \vspace*{0.5mm}
}

% Description
\newcommand{\bulletpoint}[1]{
  \begin{hyphenrules}{nohyphenation}
  	\hangindent=1.5cm \rightskip=2.35cm \tab[1.1cm] $\bullet$#1 \\
  \end{hyphenrules}
  \medskip
}

\begin{document}
  \pagestyle{empty} % Removes page numbers
  % Name and contact information.
  \flushleft{\huge{\textbf{\textcolor{lgrey}{Zachary A.} \textcolor{dgrey}{Churchill}}} 
             \hfill \footnotesize{jobs.eel683@passmail.net}}

  % Summary
  \begin{flushleft}
    \header{SUMMARY}

    \tab Resourceful Data Scientist with 7 years of hands-on experience spanning from \\
    \tab initial analytics to advanced Machine Learning operations (MLOps). Proficient in \\
    \tab Python, R, and SQL, I've driven business insights and engineered custom pipelines \\
    \tab for deploying complex data models. Eager to expand my software engineering \\
    \tab capabilities, I am keen to evolve into a full-fledged Machine Learning Engineer. \\

    \smallskip
  \end{flushleft}
  
  % Education
  \begin{flushleft}
    \header{EDUCATION}

    \textbf{Bachelor of Science in Mathematical Statistics,} \hfill Ohio University, Athens OH \\
    \textbf{Minor in Economics}

    \tab[0.5cm] Overall G.P.A:  3.82 / 4.00 \tab[0.25cm] \textit{Magna Cum Laude} \\
    \tab[0.5cm] \hspace*{2.08mm}Major G.P.A: 3.98 / 4.00  \hfill \small{*Diploma Conferred on Dec 10th, 2016}

    \smallskip
  \end{flushleft}

  % Work Experience
  \begin{flushleft}
    \header{PROFESSIONAL EXPERIENCE}

    \company{American Electric Power}{Columbus OH}{Oct 2022}{Current}
    
    \position{Principal Data Analyst (Tech Business Analyst Prin)}{Oct 2022}{Current}{Python, R, SQL, PowerBI, git}
    \bulletpoint{
    	Lead top-of-the-funnel analytics, bridging gaps through cross-team collaboration and
	swift data insights. Piloted data-driven initiatives like preventive maintenance analysis
	to optimize break-fix costs and offer timely support for the Operations and Performance
	Transformation team on enterprise projects.
    }
    \bulletpoint{
    	Champion AEP's understanding and application of Generative AI (GenAI). Delivered a
	comprehensive presentation on its potential uses, nuances like prompt engineering, and the
	imperative of data privacy.
    }
    \bulletpoint{
    	Offer expertise in MLOps from a software engineering perspective through code reviews,
	best practice recommendations, and solution brainstorming alongside solution engineers and data scientists.
    }
    \bulletpoint{
        TODO around GenAI platform and specific MLOps example around Vision ML pipelines in
        AWS SageMaker for wind turbine blade defect detection (utilized Ground Truth, fine-tuned
        AWS-provided segmentation models and created pipelines to fine-tine custom Pytorch
        scripts).
    }
    \medskip

    \company{State of Ohio - MHAS}{Columbus OH}{Mar 2022}{Sept 2022}
    
    \position{Data Scientist (Software Development Specialist 4)}{Mar 2022}{Sept 2022}{Python, SQL, PowerBI}
    \bulletpoint{
    	Spearheaded an in-depth analysis of the Grants and Funding Management System. This initiative led
	to the development of a preliminary PowerBI dashboard, offering crucial insights into grant allocations.
	This tool was designed to transparently showcase the value of grant distributions to Ohio residents.
    }

    \newpage

    \company{Root Insurance}{Columbus OH}{Feb 2019}{Feb 2022}

    \position{Data Analyst II - LTV Analytics}{Oct 2021}{Feb 2022}{SQL, R, Tableau, Mode Analytics, git}
    \bulletpoint{
	Deliver pivotal analytics support for external business inquiries centered on customer lifetime
	value (LTV) metrics. Actively design a series of executive dashboards to assess the accuracy
	and consistency of the model-generated LTV metrics.
    }

    \medskip

    \position{Software Engineer I, II - Data Science Engineering}{Mar 2020}{Sept 2021}{Python, AWS, Docker, git, BuildKite, Terraform}
    \bulletpoint{
	Sustained and enhanced the customer lifetime value prediction process by crafting internal
	packages and templates, enabling data scientists to streamline machine learning model
	deployments within AWS SageMaker.
    }
    \bulletpoint{
    	Guided the development of SageMaker Endpoint APIs and serverless infrastructure,
	strategically transitioning the user telematics score computations away from a Ruby on Rails application.
    }

    \medskip

    \position{Senior Product Analyst - Mobile App Conversion}{Feb 2019}{Feb 2020}{R, SQL, Python, AWS, Docker, git, Tableau}
    \bulletpoint{
	Established the foundational daily customer lifetime value prediction process leveraging AWS
	SageMaker, Lambda, and an internal data extraction tool. Initially designed for the growth marketing
	team, this tool became integral to the company's overarching decision-making framework.
    }
    \bulletpoint{
	Directed the analysis for pivotal A/B tests within the mobile app experience and pioneered
	the standardization of conversion A/B test analyses. Crafted an R package to facilitate a Bayesian
	analysis, streamlining the generation of consistent report outcomes for analysts.
    }

    \medskip


    \company{American Electric Power}{Columbus OH}{Jan 2017}{Feb 2019}
    
    \position{CHARGE Solutions Consultant}{Nov 2018}{Feb 2019}{Java, JavaScript, HTML, CSS, SmartSheet}
    \bulletpoint{
	Collaborated with multiple business units on targeted projects to enhance workflow efficiency
	using SmartSheet. Simultaneously underwent training in web and mobile app development technologies.
    }
    \medskip

    \position{Associated Data Scientist}{Jan 2017}{Oct 2018}{Python, R, Oracle, Linux, Docker, git}
    \bulletpoint{
    	Designed and implemented a daily statistical process for quality control, automating the prediction
	and cataloging of potential errors in transmission data for over 600 commercial customers.
	Complemented this with an Oracle APEX dashboard, streamlining the team's workflow and
	enabling efficient note-taking on predictions.
    }
    \bulletpoint{
    	Engineered a comprehensive data analysis tool alongside a discrete-event simulation program,
	offering insights into the annualized cost implications of varied predictive maintenance inspection
	strategies at the Amos power plant.
    }
    \medskip
  \end{flushleft}
  

\end{document}
